---
title: "Crawling_dsl"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Daum

library(tidyverse)
library(httr)
library(rvest)

'https://www.daum.net/'

res <- GET(url = 'https://www.daum.net/')

print(x = res)

searchWords <- res %>% 
  read_html() %>% 
  html_nodes(css = 'div.realtime_part > ol > li > div > div:nth-child(1) > span.txt_issue > a') %>% 
  html_text(trim = TRUE)

print(x = searchWords)

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(httr)
library(rvest)

'https://www.daum.net/'

res <- GET(url = 'https://www.daum.net/')

print(x = res)

searchWords <- res %>% 
  read_html() %>% 
  html_nodes(css = 'div.realtime_part > ol > li > div > div:nth-child(1) > span.txt_issue > a') %>% 
  html_text(trim = TRUE)

print(x = searchWords)
```

## Naver_Stock

library(tidyverse)
library(httr)
library(rvest)
library(stringr)

'https://finance.naver.com/sise/sise_index.nhn?code=KOSPI'

res <- GET(url = 'https://finance.naver.com/sise/sise_index.nhn?code=KOSPI')

print(x = res)

searchtable <- res %>% 
  read_html(encoding='euc-kr') %>% 
  html_nodes(css = '#contentarea_left > div.box_top_sub > div > div.subtop_sise_detail > table') %>% 
  html_table(fill = TRUE)

searchtable <- as.data.frame(searchtable)
searchtable$X1<-searchtable$X1 %>% str_remove_all(pattern = '\n|\t')
searchtable$X2<-searchtable$X2 %>% str_remove_all(pattern = '\n|\t')
searchtable$X3<-searchtable$X3 %>% str_remove_all(pattern = '\n|\t')
searchtable$X4<-searchtable$X4 %>% str_remove_all(pattern = '\n|\t')

상한<-str_sub(lastlist,-135,-130)
하한<-str_sub(lastlist,-6,-1)
상승<-str_sub(lastlist,-104,-97)
보합<-str_sub(lastlist,-71,-65)
하락<-str_sub(lastlist,-39,-32)

a<- c(상한, 상승)
b<- 보합
c<-c(하락, 하한)
searchtable$X2[4] = list(a)
searchtable$X3[4] = b
searchtable$X4[4] = list(c)


print(x = searchtable)

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(httr)
library(rvest)
library(stringr)

'https://finance.naver.com/sise/sise_index.nhn?code=KOSPI'

res <- GET(url = 'https://finance.naver.com/sise/sise_index.nhn?code=KOSPI')

print(x = res)

searchtable <- res %>% 
  read_html(encoding='euc-kr') %>% 
  html_nodes(css = '#contentarea_left > div.box_top_sub > div > div.subtop_sise_detail > table') %>% 
  html_table(fill = TRUE)

searchtable <- as.data.frame(searchtable)
searchtable$X1<-searchtable$X1 %>% str_remove_all(pattern = '\n|\t')
searchtable$X2<-searchtable$X2 %>% str_remove_all(pattern = '\n|\t')
searchtable$X3<-searchtable$X3 %>% str_remove_all(pattern = '\n|\t')
searchtable$X4<-searchtable$X4 %>% str_remove_all(pattern = '\n|\t')

lastlist<-searchtable[[2]][4]
as.character(lastlist)

상한<-str_sub(lastlist,-135,-130)
하한<-str_sub(lastlist,-6,-1)
상승<-str_sub(lastlist,-104,-97)
보합<-str_sub(lastlist,-71,-65)
하락<-str_sub(lastlist,-39,-32)

a<- c(상한, 상승)
b<- 보합
c<-c(하락, 하한)
searchtable$X2[4] = list(a)
searchtable$X3[4] = b
searchtable$X4[4] = list(c)


print(x = searchtable)
```

